Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-19 paper/paper.tex
Flesh out conclusion a bit

Some immoral perspectives on closely coupling branching with a particular constraint. Whether this
is useful for other things, like ASP.

Adapting clique algorithms: specialised inference, association-aware bound function, .

SIP invariants when very similar graphs (except these are easy).

@@

@@

Possibly portfolios.

Parallel. ?? Stuff on EHPs, how work stealing matters here too \cite{DBLP:journals/jco/BatsynGMP14,DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16}

\cite{DBLP:conf/ictai/MinotNS15}

>>>>

We have seen that a modern clique algorithm can perform competitively for maximum common subgraph
problems, particularly when edge labels are involved.

We believe there is further scope for tailoring clique algorithms for association graphs.
Specialised inference, association-aware bound function. Treating the first branch specially, since
it will eliminate so much of the search space \cite{DBLP:conf/cocoon/SutersAZSSL05}.

For CP models for the connected version of the problem, we saw the benefits of combining
conventional filtering with a special branching rule. Using a branching rule for correctness, rather
than simply as an ordering heuristic, is unconventional and does not cleanly fit into the
abstractions used by toolkits.

We looked only at single-threaded versions of these algorithms. Maximum clique algorithms have been
extended for thread-parallel search
\cite{DBLP:journals/algorithms/McCreeshP13,DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16}.
In particular, EHPs \cite{DBLP:journals/topc/McCreeshP15}. On the CP side, decomposition \cite{DBLP:conf/ictai/MinotNS15}.

@@

Symmetries. Dynamic.

@@
